---
title: "IREX 10: Identification Track"
output:
   html_document:
      self_contained: no
      fig_caption: yes
      number_sections: false
      includes:
         before_body: header.html
         after_body: footer.html
      css: ['nist.css', 'irex10.css']
      theme: null
      highlight: null
      mathjax: null
header-includes:
   - \usepackage{svg} 
   - \hypersetup{colorlinks=true}
   - allbordercolors={0 0 0}
params:
   test: 'ops4/timing'
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(irex10)
library(knitr)
library(DT)           # for interactive tables
options(scipen = 9)   # discourage conversion of raw numbers to scientific notation.

test <- params$test

matchers <- setdiff(matchers, c('Stub/20190820', 'Sift/20190820', 'Flynn/20200102',
                                'Idemia/20191203'))

size <- "500K people" # -GW
eyes <- "Both eyes"   # -GW
enrollment.mode <- 'One enrollment session per person' # -GW

search.file <- get.property(test, 'Input CSV', 'search')
searches    <- fread(search.file, fill = TRUE, sep = " ", header = FALSE)$V1

num.searches <- format(nrow(searches), big.mark = '\u2006', small.mark = '\u2006',
                       scientific = FALSE, format = 'f')
```

<!-- Display social media icons just under the title -->
```{r child = 'socialMediaIcons.html'}
```

## Creation Times

Computation times are measured as the the elapsed real time (i.e., "wall clock" time) as opposed to CPU time. Timing estimates were computed on unloaded machines with only a single process dedicated to biometric operations. The test machines are
<A href="https://www.dell.com/downloads/global/products/pedge/M910_Spec_Sheet.pdf">Dell PowerEdge M910</A> blades with Dual Intel Xeon X7560 2.3 GHz CPUs (eight cores per processor).

<TABLE style='margin-bottom:20px;font-size:15px;line-height:1'>
 <TR><TD>Dataset:</TD><TD><A href=''><B><I>Operational Dataset 4</I></B></A></TD></TR>
 <TR><TD>Samples used:</TD><TD><B><I>`r eyes`</I></B></TD></TR>
 <TR><TD>Enrolled Population:</TD><TD><B><I>`r size`</I></B></TD></TR>
 <TR><TD style='margin-bottom:5px'>Enrollment Method:</TD><TD><B><I>`r enrollment.mode`</I></B></TD></TR>
 <TR><TD>Number of Searches:</TD><TD><B><I>`r num.searches`</I></B></TD></TR>
</TABLE>

<P style='margin-left:30px'>
```{r fig.width = 8, fig.height = 2}
# Search statistics.
data  <- SJ(test = "ops4/timing", matcher = matchers)
data <- data[, get.template.stats(test, matcher), by = .(test, matcher)]

boxplot.template.times(data)
```
</P>

